---
title: "Homework 5"
author: "Hao Xu"
date: "11/20/2021"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(readr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

For this problem, we are interested in data gathered and made public by _The Washington Post_ on homicides in 50 large U.S. cities. The code chunk below imports and cleans the data.

```{r}
homicide_df = 
  read_csv("./files/homicide-data.csv", na = c("", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

Now focus on Baltimore, MD.

```{r}
baltimore_df = 
  homicide_df %>% 
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>% 
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(
  x = baltimore_summary %>% pull(unsolved),
  n = baltimore_summary %>% pull(n)
)

baltimore_test %>% 
  broom::tidy()
```

Write a function to test other cities.

```{r}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>% 
    summarise(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
}
```

Iterate across cities

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

knitr::kable(results_df)
```

Make the plot

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

Finally get the number of unresolved and total, for each city.

```{r}
homicide_df %>% 
  group_by(city_state) %>% 
  summarise(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>% 
  knitr::kable()
```

# Problem 2

First get all the file names:

```{r}
zipdata = tibble(
  files = list.files("./files/data/")
)
```

Use the map function to get the relative directory for each file

```{r}
directory = map(.x = zipdata[[1]], ~str_c("./files/data/", .x)) %>% unlist()
```

Now get the data from each file, create variable indicating the arm and id, and other cleaning process

```{r message = FALSE}
complete_data = zipdata %>% 
  mutate(
    datas = map(.x = directory, ~read_csv(.x))
  ) %>% 
  unnest(datas) %>% 
  
  #separate the file variable to get subject ID
  separate(files, into = c("subject_id"), sep = 6) %>% 
  
  #get the arms, but still keep the subject_id
  separate(subject_id, into = "arm", sep = 3, remove = FALSE) %>% 
  
  #rename the variables in "arm"
  mutate(
    arm = fct_recode(arm, "control" = "con",
                          "experimental" = "exp")
  ) %>% 
  
  #use pivot_longer
  pivot_longer(week_1:week_8, names_to = "week_number", values_to = "observation") %>% 
  
  #remove the "week_" in each cell of the variable "week_number"
  mutate(week_number = str_replace(week_number, "week_", ""),
         week_number = as.numeric(week_number))
```

Now get the spaghetti plot

```{r}
complete_data %>% 
  ggplot(aes(x = week_number, y = observation, color = arm)) +
  geom_line(aes(group = subject_id)) +
  labs(
    x = "Week Number",
    title = "spaghetti plot of observations for each subject"
  )
```

As we can see on the plot, the experimental group has generally larger observation than the control group, and we could conclude that the thing we are experimenting is effective.

